\textbf{Matching the forecast horizon with the relevant spatial and temporal processes and data sources}

### 2020-04-01 doc/manuscript.tex
revising code 4 nonstationarity

Our \new{simulation studies} have important implications for the emerging field of ecological forecasting. First, they suggest that evaluating model performance at both short and long forecsat horizons will be essential as research on forecasting methods accelerates. Second, while single approaches may perform reasonably well for either short or long horizons, skillful predictions at intermediate forecast horizons may require a combination of information from spatial and temporal statistical models. Intermediate time horizons pose challenges in other forecasting contexts as well. Weather forecasts based on regional-scale meteorological models are very effective for forecasting a week to ten days in advance, but then become largely uninformative. Forecasting these intermediate scales has been challenging in meteorology and will likely be challenging in ecology as well. While the recent emphasis on near-term iterative forecasting \citep{dietze_iterative_2018} is the logical and tractable starting point, we also need to build understanding and capacity for forecasting ecological dynamics across all forecast horizons of interest.

>>>>

Our \new{simulation studies} have important implications for the emerging field of ecological forecasting. First, they suggest that evaluating model performance at both short and long forecast horizons will be essential as research on forecasting methods accelerates. Second, while single approaches may perform reasonably well for either short or long horizons, skillful predictions at intermediate forecast horizons may require a combination of information from spatial and temporal statistical models. Intermediate time horizons pose challenges in other forecasting contexts as well. Weather forecasts based on regional-scale meteorological models are very effective for forecasting a week to ten days in advance, but then become largely uninformative. Forecasting these intermediate scales has been challenging in meteorology and will likely be challenging in ecology as well. While the recent emphasis on near-term iterative forecasting \citep{dietze_iterative_2018} is the logical and tractable starting point, we also need to build understanding and capacity for forecasting ecological dynamics across all forecast horizons of interest.
